\documentclass[a4paper, titlepage, 12pt]{article}

% XXX sa saad kaitsmisel nalja teha kui tahad ja märkida, et kuigi wikipedia
% viiteid ei loeta heaks tooniks, ei õnnestunud sul tööd ilma teha, sest nende API on
% paraku wikis kirjeldatud

\usepackage{utf8}

\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{hyphenat}
\usepackage{parskip}
\usepackage[nottoc]{tocbibind}
\usepackage{graphicx}
\usepackage{lastpage}
\usepackage{tabulary}

\graphicspath{ {img/} }

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\DeclareUnicodeCharacter{00A0}{ }

\newcommand{\pypy}{PyPy}
\newcommand{\bulletsection}[1]{\section*{#1}
\addcontentsline{toc}{section}{#1}}

\begin{document}
\include{tex/title}

\begin{abstract}
The Estonian Wikipedia has a lot of articles that are of high-quality, but are
hard to find from the huge set of articles. The aim of this
thesis is to filter out the high-quality articles from the low-quality ones
using a machine learning algorithm called logistic regression.

The main problem was filtering out the high-quality articles from the
low-quality articles. An algorithm was written using gradient descent to find
the logistic regression weights from a matrix of numerical data. Therefore,
the main tasks of this thesis were to find known high-quality articles and known
low-quality Wikipedia articles, translate them into numerical data, train the
machine learning algorithm in a small enough number of iterations and validate
the accuracy of this algorithm.

Research shows that the Estonian Wikipedia has a category for hand-picked
high-quality articles and a way to obtain a random article, which will labeled
as low-quality. Training the algorithm with those results, the accuracy of the
result is enough to filter out high-quality articles out of all of the Estonian
Wikipedia.

% TODO Put the right data in.
The thesis is in English and contains \pageref*{LastPage} pages of text,
[chapters] chapters, [figures] figures, [tables] tables., etc.
\end{abstract}

\listoftables
\clearpage

\listoffigures
\clearpage

\tableofcontents
\clearpage

\include{tex/introduction}
\include{tex/tools}
\include{tex/analyser}
\include{tex/results}

\bulletsection{Summary}
The aim of this thesis is to provide a way to filter out the high-quality
articles in the Estonian Wikipedia. The best way to do so would be using
logistic regression, a machine learning algorithm.

The Estonian Wikipedia has a hand-picked category for high-quality articles.
The machine learning algorithm can be trained with these articles. Logistic
regression has a weight for each feature or dimension of the article. Logistic
regression is also blind to data type and only sees the scalar value. That
means that it is impossible to identify whether an article uses a certain kind
of template or has certain words or characters in it.

An article has 7 features: characters, pages that refer it, pages that it refers
to, images it refers to, external links it contains, templates it links to,
categories it is in. These features were selected because they were readily
available through the PyWikiBot framework. Because logistic regression accepts
only scalar values, the count of each feature was used. A 8th constant weight is
added as a prefix to counteract the bias in the data.

An algorithm was written using gradient descent to find the logistic regression
weights from the matrix of numerical data. Gradient descent is an algorithm to
calculate the local minimum or maximum of a range of data. In this case, we want
to find the minimum of the error rate. It iterates over the last result and
changes it towards the local minimum. The size of the step of each iteration
must be carefully chosen or the algorithm might step over the local minimum
without lowering the deviation.

When the data has a great bias or big deviations, gradient descent must go
through a lot of iterations to negate that. By normalising the data beforehand,
all the features have the same small bias and deviation. This is also done in
this thesis, otherwise the iteration count might grow so large, that it is hard
to differentiate between a forever looping algorithm and an eventually stopping
algorithm.

Validation is done by setting aside 30\% of the articles gathered for training
and then comparing the label the algorithm predicted for these articles with
their true label.

The average error rate of the algorithm detailed in this thesis is 2.22\%. This
is achieved with averagly 714.8 iterations of gradient descent. This error rate
can be considered good enough for the purposes of the editors in Vikipeedia.

One possible improvement is not using the PyWikiBot framework. Because of the
way the PyWikiBot framework's interface works the program queries more times from
the MediaWiki server than is required. Each article has a summary page about the
article's metadata, which can be screen scraped to get most of the required
features with one query. It is also possible to make one specific query through
the MediaWiki API to get the required metadata.

Another possible improvement is to subjectively separate bad articles
and use that data to teach the machine learning algorithm. In this thesis
separating the high-quality articles was done because the high-quality articles
were already handpicked by the Vikipeedia editors. The logistic regression
algorithm can also be made to accept multiple classifications instead of 2.

I conclude that it is entirely possible to use machine learning to sift out
the high-quality articles.

\bibliographystyle{plain}
\bibliography{loputoo}

\end{document}